Bootstrapping Multi-atlas Segmentation Using Multiple Automatically Generated Templates for the Segmentation of the Whole Hippocampus and Subfields

### 2013-12-29 paper.Rnw
Added latest FEP xval results

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ADNI1-XVAL: mean Kappa plot by atlases, templates, reg and voting method. 
\begin{figure}
<<fig:FEP-xval-k-mean, cache=TRUE, dependson='ADNI1-xval-load', fig.width=7, fig.height=7>>=
fep.xval <- subset(read.csv('data/results-fep-xval-ants-2013-12-28-020512.csv'),
                   k > 0.5)
fep.xval$atlases <- as.factor(fep.xval$atlases)
fep.xval.mean <- ddply(fep.xval, .(subject,atlases,templates,label), function (df) {
  data.frame(k=mean(df$k),volume=mean(df$volume))
})
stderr <- function(x) sqrt(var(x)/length(x))
ggplot(fep.xval.mean, aes(x=templates,y=k, colour=atlases)) + 
  stat_summary(fun.y=mean,geom='line', aes(y=k,weight=1,group=atlases)) + 
  stat_summary(fun.y=mean,geom='point',aes(y=k,weight=1,group=atlases)) + 
  stat_summary(fun.y=mean,
               fun.ymin=function (x) mean(x) - stderr(x),
               fun.ymax=function (x) mean(x) + stderr(x), 
               geom='errorbar',aes(y=k, weight=1, group=atlases), 
               linetype='solid', width=0.5) + 
  #stat_smooth(method='lm', formula=y~log(x)) + 
  scale_y_continuous(breaks=seq(0,1,0.01)) + 
  scale_colour_hue(name="Number of Atlases") +
  scale_linetype(name="Registration Method") +
  xlab( "Number of Templates" ) + 
  ylab( "Mean similarity (DSC)" ) + 
  theme(legend.direction = "horizontal", legend.position = "bottom", 
        axis.text = element_text(size = 8))
@
  \caption{Mean Dice's Similarity Coefficient of \mb{} unilateral hippocampal 
  segmentations relative to
  \psegs{} for 81 FEP subjects vs. atlas and template library
  size using \ants registration algorithm and majority vote label fusion method 
  over 3 folds of Monte Carlo cross validation. 
  Error bars indicate standard error.
  \label{fig:FEP-xval-k-mean}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ADNI1-XVAL: mean Kappa plot by atlases, templates, reg and voting method. 
\begin{figure}
<<fig:FEP-xval-k-mean, cache=TRUE, dependson='ADNI1-xval-load', fig.width=7, fig.height=7>>=
fep.xval <-subset(read.csv('data/results-fep-xval-ants-2013-12-28-223825.csv'), k > 0.5)
fep.xval$atlases <- as.factor(fep.xval$atlases)
fep.xval.mean <- ddply(fep.xval, .(subject,atlases,templates,label), function (df) {
  data.frame(k=mean(df$k),volume=mean(df$volume))
})
stderr <- function(x) sqrt(var(x)/length(x))
ggplot(fep.xval.mean, aes(x=templates,y=k, colour=atlases)) + 
  stat_summary(fun.y=mean,geom='line', aes(y=k,weight=1,group=atlases)) + 
  stat_summary(fun.y=mean,geom='point',aes(y=k,weight=1,group=atlases)) + 
  stat_summary(fun.y=mean,
               fun.ymin=function (x) mean(x) - stderr(x),
               fun.ymax=function (x) mean(x) + stderr(x), 
               geom='errorbar',aes(y=k, weight=1, group=atlases), 
               linetype='solid', width=0.5) + 
  #stat_smooth(method='lm', formula=y~log(x)) + 
  scale_y_continuous(breaks=seq(0,1,0.01)) + 
  scale_colour_hue(name="Number of Atlases") +
  scale_linetype(name="Registration Method") +
  xlab( "Number of Templates" ) + 
  ylab( "Mean similarity (DSC)" ) + 
  theme(legend.direction = "horizontal", legend.position = "bottom", 
        axis.text = element_text(size = 8))
@
  \caption{Mean Dice's Similarity Coefficient of \mb{} unilateral hippocampal 
  segmentations relative to
  \psegs{} for 81 FEP subjects vs. atlas and template library
  size using \ants registration algorithm and majority vote label fusion method 
  over 3 folds of Monte Carlo cross validation. 
  Error bars indicate standard error.
  \label{fig:FEP-xval-k-mean}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
